---
title: "Introduction to using here"
author: "Shane Dewees"
date: "2023-01-23"
output: html_document
---

WOAH CRAZY WOW SPOOKY CHANGES


As long as you're working in R studio, for reading and writing, here will work

benefit for switching between macs and pcs and compatibility
it can maybe handle spaces?

lose tab completion

lee ran into issues inside functions - running source script that was writing a file

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
```
Note how here automatically starts in the folder of R project as mentioned above. 

Instead of setting working directory, we can just use the function here inside read.csv. It is super easy, pretty awesome, and makes the code reproducible on other computers. 
```{r}
awesome_data <- read.csv(here("awesome_data.csv"))
awesome_data
```
Lets delete the words column and then save the new csv also using here().
  - we will also see how to reference folders
```{r}
even_awesomer_data <- awesome_data %>% 
  select(!words)

write.csv(even_awesomer_data, here("data", "even_awesomer_data.csv")) # to add another sub folder, just another comma ""
```

Ta da!